The Free-play Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-06 paper.tex
Finished social annotations

Annotating social interaction beyond surface behaviours is generally difficult:
The observable, surface behaviours typically result of a superposition of the
complex and non-observable underlying cognitive and emotional states. As
such, these deeper socio-cognitive states can only be indirectly observed,
and their labelling is typically error prone.

Our aim is to provide insights on the social dynamics, and we have synthesised a
new coding scheme for social interactions that reuse and adapt three established
social scales. Our coding scheme (Figure~\ref{fig|coding-scheme}) looks specifically
at three axis: the level of \emph{task engagement} (that distinguishes between
\emph{focused}, \emph{task oriented} behaviours, and \emph{disengaged} -- yet
sometimes highly social -- behaviours); the level of social engagement (reusing
Parten's stages of play, but at the micro-task level); the social attitude (that
encode attitudes like \emph{supportive}, \emph{aggressive}, \emph{dominant},
\emph{annoyed}, etc.)

@@

@@

In our scheme, we characterise \emph{Social engagement} by building upon
Parten's stages of play. These 5 stages of play are normally
used to characterise rather long sequences (at least several minutes) of social
interactions.

However, instead of characterising long social
sequences (several minutes) with these 5 stages, we look at the micro-structure of the
interaction:

>>>>

Annotating social interaction beyond surface behaviours is generally difficult.
The observable, surface behaviours typically result of a superposition of the
complex and non-observable underlying cognitive and emotional states. As
such, these deeper socio-cognitive states can only be indirectly observed,
and their labelling is typically error prone.

Our aim is to provide insights on the social dynamics, and we have synthesised a
new coding scheme for social interactions that reuse and adapt established
social scales. Our coding scheme (Figure~\ref{fig|coding-scheme}) looks specifically
at three axis: the level of \emph{task engagement} (that distinguishes between
\emph{focused}, \emph{task oriented} behaviours, and \emph{disengaged} -- yet
sometimes highly social -- behaviours); the level of social engagement (reusing
Parten's stages of play, but at the micro-task level); the social attitude (that
encode attitudes like \emph{supportive}, \emph{aggressive}, \emph{dominant},
\emph{annoyed}, etc.)

@@

\paragraph{Task engagement}

The first axis of our coding scheme aims at making a broad distinction between
`on-task' behaviours (even tough the free-play sandbox does not explicitly
require the children to perform a specific task, they are still engaged in an
underlying task: to play with the game) and `off-task' behaviours. We call
`on-task' behaviours \emph{goal oriented}: they encompass considered, planned
actions (that might be social or not). \emph{Aimless} behaviours (with respect
to the task) encompass opposite behaviours: being silly, chatting about
unrelated matters, having a good laugh, etc. These \emph{Aimless} behaviours are
in fact often highly social, and play an important role in establishing trust
and cooperation between the peers. In that sense, they should not be discarded.

@@

In our scheme, we characterise \emph{Social engagement} by building upon
Parten's stages of play. These 5 stages of play are normally
used to characterise rather long sequences (at least several minutes) of social
interactions. Here, we apply them at the level of each of the micro-sequences of
the interactions: one child is drawing and the other is observing is labelled as
\emph{solitary play} for the former child, \emph{on-looker} behaviour for the
later; the two children discuss what to do next: this sequence is annotated as
a \emph{cooperative} behaviour; etc.

By suggesting such a fine-grained coding of social engagement, we enable proper
analyses of the internal dynamics of a long sequence of social interaction.
